Something something progress in light

### 2022-07-28 2_SSL_EES/article/article_supplementary.tex
beautification and fixed bib file

\cite{Murphy2012} Note that this is in contrast to the original value given in \cite{azevedo2009transition}. 
Note that a humorous illustration of this trend in this figure has been provided by Randall Munroe in \href{https://xkcd.com/1603/}{https://xkcd.com/1603/}.

@@

Consumer organization magazines:

\textit{Stiftung Warentest (Germany)}: \cite{Warentest2008}\cite{Warentest2009_1}\cite{Warentest2009_2}\cite{Warentest2010_1}\cite{Warentest2010_2}\cite{Warentest2011}\cite{Warentest2012}\cite{Warentest2013}\cite{Warentest2014_1}\cite{Warentest2014_2}\cite{Warentest2015}\cite{Warentest2016_1}\cite{Warentest2016_2}\cite{Warentest2018}

\textit{Konsument (Austria)}: \cite{Konsument2010}

\textit{Which (UK):} \cite{Which2020})

Industry periodicals:

@@

Support by German consumer organization Stiftung Warentest in providing access to their archive is gratefully acknowledged.
Figure XX (Historical evolution of light-emitting diode chip architectures)

Scientific publications:

@@

Patents:
\href{https://worldwide.espacenet.com/patent/search?q=pn%3DJPH11168235A}{JPH11168235A}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn%3DDE19921987A1}{DE19921987A1}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn%3DJPH11340514A}{JPH11340514A}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn%3DJP2001044498A}{JP2001044498A}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn%3DUS2005045893A1}{US2005045893A1}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn%3DUS2002093023A1}{US2002093023A1}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn%3DUS2006273339A1}{US2006273339A1}

Other publications:

https://web.archive.org/web/20170801160530/
https://www.energy.gov/sites/prod/files/2015/02/f19/craford_innovation_sanfrancisco2015.pdf
https://web.archive.org/web/20170715230721/https://www.energy.gov/sites/prod/files/2016/02/f29/sun_china_raleigh2016.pdf
http://web.archive.org/web/20160425025936/
https://www.slideshare.net/Yole_Developpement/yole-led-packagingjanuary2013reportsample

Figure XX (Historical developments in the device sub-efficiencies):

The complete list of sources for the figure provided below is organized by the sub-efficiencies (panels) described in the figure.

Forward Voltage (panel a):

@@

Internal Quantum Efficiency (panel b):

@@

Average performance and future targets set by the U.S. Department of Energy (DoE) derived from industry round-table discussions:

@@

Note that the artifact in the DoE Average around 2013 is due to a change in definition for internal quantum efficiency laid out in \cite{doe_ssl_multiyear_2013}

Droop (panel c):

Data calculated from luminous intensity curves of respective device datasheets. Sources for datapoints:

\cite{datasheet_osram_topled}\cite{osram2008data}\cite{osram2008gdplus}\cite{osram2018csp}\cite{datasheet_lumileds_lux1}\cite{lumi2008data}\cite{lumi2016data_1}\cite{lumi2016data_2}\cite{samsung2018data} \\ Sources for DoE data: \cite{doe_ssl_multiyear_2010}\cite{doe_ssl_multiyear_2011}\cite{doe_ssl_multiyear_2012}\cite{doe_ssl_multiyear_2013}\cite{doe_ssl_multiyear_2014}\cite{doe_ssl_rnd_2015}\cite{doe_ssl_rnd_2016}

Light-Extraction Efficiency (panel d):

\cite{lee2005analysis}\cite{krames2007status}\cite{Jang2004}\cite{Horng2013}\cite{Liao2010}\cite{HungWenHuang2005}\cite{Leem2007}\cite{Huang2008}\cite{Wang2009}\cite{Huh2003}\cite{Horng2008}\cite{Gao2008}\cite{Chang2003}\cite{Zhou2012}\cite{ChunJuTun2006}\cite{Hua2009}\cite{Matioli2010}\cite{lee2005analysis}\cite{Zhu2015}\cite{Ding2015}\cite{Taki2019}\cite{Shchekin2006}\cite{Hu2016}\cite{Horng2010}\cite{Lin2016}\cite{Yue2018}\cite{Zhao2012}\cite{Zhu2015}\cite{Ding2015}\cite{wierer2001high}\cite{Steigerwald2002}\cite{DaeSeobHan2006}\cite{Wang2006}\cite{Lee2007}\cite{Shen2007}\cite{Huang2006}\cite{Zhmakin2011}

>>>>

\cite{Murphy2012}

Note that this is in contrast to the original value given in \cite{azevedo2009transition}. 
Note that a humorous illustration of this trend in this figure has been provided by Randall Munroe in \href{https://xkcd.com/1603/}{https://xkcd.com/1603/}.

@@

The complete list of sources is organized by different sources:

\subsubsection{Consumer organization magazines}

Stiftung Warentest (Germany): \cite{Warentest2008}\cite{Warentest2009_1}\cite{Warentest2009_2}\cite{Warentest2010_1}\cite{Warentest2010_2}\cite{Warentest2011}\cite{Warentest2012}\cite{Warentest2013}\cite{Warentest2014_1}\cite{Warentest2014_2}\cite{Warentest2015}\cite{Warentest2016_1}\cite{Warentest2016_2}\cite{Warentest2018}

Konsument (Austria): \cite{Konsument2010}

Which (UK): \cite{Which2020}

\subsubsection{Industry periodicals}

@@

Support by German consumer organization Stiftung Warentest in providing access to their archive is gratefully acknowledged.

\subsection{Figure XX (Historical evolution of light-emitting diode chip architectures)}

\subsubsection{Scientific publications}

The complete list of sources is organized by different sources:

@@

\subsubsection{Patents}

\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DJPH11168235A}{JPH11168235A}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DDE19921987A1}{DE19921987A1}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DJPH11340514A}{JPH11340514A}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DJP2001044498A}{JP2001044498A}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DUS2005045893A1}{US2005045893A1}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DUS2002093023A1}{US2002093023A1}, 
\href{https://worldwide.espacenet.com/patent/search?q=pn\%3DUS2006273339A1}{US2006273339A1}

\subsubsection{Other publications}

\href{https://web.archive.org/web/20170801160530/https://www.energy.gov/sites/prod/files/2015/02/f19/craford_innovation_sanfrancisco2015.pdf}{2015 presentation (www.energy.gov)}
\href{https://web.archive.org/web/20170715230721/https://www.energy.gov/sites/prod/files/2016/02/f29/sun_china_raleigh2016.pdf}{2016 presentation (www.energy.gov)}
\href{http://web.archive.org/web/20160425025936/https://www.slideshare.net/Yole_Developpement/yole-led-packagingjanuary2013reportsample}{2013 presentation (www.slideshare.net)}

\subsection{Figure XX (Historical developments in the device sub-efficiencies)}

The complete list of sources is organized by the sub-efficiencies (panels) described in the figure:

\subsubsection{Forward Voltage (panel a)}

@@

\subsubsection{Internal Quantum Efficiency (panel b)}

@@

Average performance and future targets set by the U.S. Department of Energy (DOE) derived from industry round-table discussions:

@@

Note that the artifact in the DOE Average around 2013 is due to a change in definition for internal quantum efficiency laid out in \cite{doe_ssl_multiyear_2013}

\subsubsection{Droop (panel c)}

Data calculated from luminous intensity curves of respective device datasheets.

Sources for datapoints: \cite{datasheet_osram_topled}\cite{osram2008data}\cite{osram2008gdplus}\cite{osram2018csp}\cite{datasheet_lumileds_lux1}\cite{lumi2008data}\cite{lumi2016data_1}\cite{lumi2016data_2}\cite{samsung2018data}

Sources for DOE data: \cite{doe_ssl_multiyear_2010}\cite{doe_ssl_multiyear_2011}\cite{doe_ssl_multiyear_2012}\cite{doe_ssl_multiyear_2013}\cite{doe_ssl_multiyear_2014}\cite{doe_ssl_rnd_2015}\cite{doe_ssl_rnd_2016}

\subsubsection{Light-Extraction Efficiency (panel d)}

\cite{lee2005analysis}\cite{krames2007status}\cite{Jang2004}\cite{Horng2013}\cite{Liao2010}\cite{HungWenHuang2005}\cite{Leem2007}\cite{Huang2008}\cite{Wang2009}\cite{Huh2003}\cite{Horng2008}\cite{Gao2008}\cite{Chang2003}\cite{Zhou2012}\cite{ChunJuTun2006}\cite{Hua2009}\cite{Matioli2010} \newline
\cite{lee2005analysis}\cite{Zhu2015}\cite{Ding2015}\cite{Taki2019}\cite{Shchekin2006}\cite{Hu2016}\cite{Horng2010}\cite{Lin2016}\cite{Yue2018}\cite{Zhao2012}\cite{Zhu2015}\cite{Ding2015}\cite{wierer2001high}\cite{Steigerwald2002}\cite{DaeSeobHan2006}\cite{Wang2006}\cite{Lee2007}\cite{Shen2007}\cite{Huang2006}\cite{Zhmakin2011}
